---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multiplyColumn

<!-- badges: start -->
<!-- badges: end -->

This package currently contains one function named multiplyColumn, which takes a data frame, a column name (whose entries are numeric), and a numeric value. It creates a new column that multiplies the entries of the specified column with the input factor and returns the data frame with this new column, as well as a histogram of the new column.

## Installation

You can install the development version of multiplyColumn from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("NaitongChen/multiplyColumn")
```

## Example

The following contains two example usages along with their outputs of the only function in the multiplyColumn package.

```{r}
# load packages
library(multiplyColumn)

# create data frame 
df = data.frame(matrix(rnorm(4),
        ncol=2, nrow=2,
        dimnames=list(NULL, c("x1","x2"))))

# examples
multiplyColumn(df, "x1", 0.5)
multiplyColumn(df, "x2", 3)
```
